\LARGE \bf Preparation of Papers for IEEE Sponsored Conferences \& Symposia*

### 2017-06-11 bmc_section.tex
Fix typo

\paragraph{Explicit path exploration.}
The second algorithm does not encode the reachability problem
$\mathsf{BoundedModelCheck}$ of a fixed length path as a single
satisfiability query, but it explicitly enumerates
the (abstract) paths in the graph that has $\Cells$
as nodes, and $\CellEdges$ as edges, and may end in an unsafe state
$\UnsafeStates$.
%
Such paths may not be real paths of
$\RTSAbstraction{\epsilon}{\System}$, since they may not satisfy the
conditions imposed by the labeling function $\CellLabelingFunction$
and the relation $\EdgeLabelingFunction$, and hence the algorithm must
further check, for each abstract path $\abspathbmc$, if tere exists a 
concrete path $\Pi$ of
$\RTSAbstraction{\epsilon}{\System}$.

>>>>

\paragraph{Explicit path exploration.}
The second algorithm does not encode the reachability problem
$\mathsf{BoundedModelCheck}$ of a fixed length path as a single
satisfiability query, but it explicitly enumerates
the (abstract) paths in the graph that has $\Cells$
as nodes, and $\CellEdges$ as edges, and may end in an unsafe state
$\UnsafeStates$.
%
Such paths may not be real paths of
$\RTSAbstraction{\epsilon}{\System}$, since they may not satisfy the
conditions imposed by the labeling function $\CellLabelingFunction$
and the relation $\EdgeLabelingFunction$, and hence the algorithm must
further check, for each abstract path $\abspathbmc$, if there exists a 
concrete path $\Pi$ of
$\RTSAbstraction{\epsilon}{\System}$.
